Exploring the Usefulness of Varactor loaded Nonlinear Transmission Lines

### 2020-06-02 RohdeAndSchwarzWhitePaper/Draft_White_Paper.tex
editedSchematic and updated report

\subsection{Rise Time}

@@

Before grappling with these issues, we were able to measure this pulse sharpening effect using a higher bandwidth oscilloscope as shown in figure \ref{fig:RandSScope}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Risetime_RandS}
\caption{Risetime can be seen to be reduced by our transmission line}
\label{fig:RandSScope}
\end{figure}

@@

>>>>

\subsection{AC Response}\label{ACMeasResults}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Board1/MeasuredACResponseB1.BMP}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

\subsection{Rise Time}\label{RiseTimeMeasResults}

@@

Before grappling with these issues, we were able to measure this pulse sharpening effect using a higher bandwidth oscilloscope as shown in figure \ref{fig:FirstRandS}.

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{Risetime_RandS}
\caption{Risetime can be seen to be reduced by our transmission line}
\label{fig:FirstRandS}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.45\textwidth]{}
\caption{}
\label{}
\end{figure}

@@

\
